---
title: "PostProcessR"
author: "Rose Abramoff"
date: "4/13/2018"
output: html_document
---
```
This script outputs customizable model predictions from one grid cell (Blodgett Forest) using ELM-Betr-ECACNP with ReSOM and/or Century to check model performance and compare against data collected at Blodgett Forest TES SFA Soil Warming Experiment.
```
#Load packages
```{r}
library(ncdf4)
library(stringr)
```

#Specify directories
```{r}
datadir <- "/Users/rzabramoff/Documents/ELMBeTRReSOM_Documentation/data_sheets/" #Blogett data directory
rundir = "/Users/rzabramoff/Documents/BigModels/runs_from_edison/" #model output directory
```

#Load data and model output with diagnostic plots
##Read in Blodgett data
```
This script reads in various Blodgett Forest data into data frames.
```
```{r}
#soil C stock data from initial pit characterization
df <- read.csv(paste0(datadir,"Blodgett_pit_C_stock_10302018.csv"))
df$MatchDepth <- df$Mid.Depth

#old gas well data from caitlin
cf <- read.csv(paste0(datadir,"ISCNtemplate_BLWarmingExperiment_1.csv"))
cf <- cf[cf$profile_name =="1Control" | cf$profile_name =="2Control" | cf$profile_name =="3Control",]
cf$CO2 <- as.numeric(as.character(cf$c_conc_CO2))
cf$time_series <- strptime(cf$gas_time_series, format = "%m/%d/%y %R" )
cf$Depth <- as.numeric(as.character(cf$layer_name))

#new gas well data from jenny
af <- read.csv(paste0(datadir,"BL_GW_all_20180712.csv"))
af$time_series <- strptime(af$Date, format = "%m/%d/%y" )
hf <- af[af$Treatment =="Heated",]
hf$time_series <- strptime(hf$Date, format = "%m/%d/%y" )
cf <- af[af$Treatment =="Control",]
cf$time_series <- strptime(cf$Date, format = "%m/%d/%y" )

#microbial biomass data from jenny
micbio <- read.csv(paste0(datadir,"MB_JS.csv"))
mbc <- micbio[micbio$Treatment=="C",]
mbc$MatchDepth <- mbc$MidDepth

#bulk density #added MatchDepth column that represents closest depth increment to relevant increments for microbial biomass - in future, interpolate
bd <- read.csv(paste0(datadir,"Blodgett_pit_C_bulk_density.csv"))
mbd <- merge(mbc,bd, by="MatchDepth")
mbd$micgram <- 100*mbd$MBC/mbd$BD_gC_cm3 #mg/g soil to gC/m2

lf <- read.csv(paste0(datadir,"BL_Lys_All.csv"))

auto <- read.csv(paste0(datadir,"BLAutoFluxAll_Aug2018.csv"))
auto$time_series <- strptime(auto$date, format = "%m/%d/%y %R")
control <- subset(auto,Plot=="BLPP1C" | Plot=="BLPP2C" | Plot=="BLPP3C") 
heated  <- subset(auto,Plot=="BLPP1H" | Plot=="BLPP2H" | Plot=="BLPP3H") 
```

##Load summary model output
```{r}
folder = c("NSC_ambient1","CEC","NSCEAH","NSCEWH") #name of folder
nyear = c(1091, 1191, 1, 1) #number of years of model run
nskip = c(10, 10, 1, 1) #number of years skipped between output files
ntype = c("yr","yr","dy","dy") #frequency of output
deepmat=NULL
out.string <- c("TOTSOMC","TOTSOMC_1m","TOTECOSYSC","TOTVEGC","LAISHA","LAISUN","GPP","HR","NPP","TSOI_10CM","TOTLITC","TOTLITC_1m") #output variables
noutputs <- length(out.string)
out.soil=in.soil=NULL

for (j in 1:length(nyear)) {
yraw <- seq(1,nyear[j],by=nskip[j])
y <- str_pad(yraw, 4, pad = "0")
for(i in 1:noutputs){
in.soil[[i]] <- vector(length = length(yraw))
}

index = 1
for (i in 1:length(y)) {
filename <- NULL
  if(ntype[j]=="yr"){
        filename <- paste(rundir,folder[j],"/",folder[j],".clm2.h0.", y[i], "-01-01-00000.nc", sep = "")
  }else if (ntype[j]=="dy") {
        filename <- paste(rundir,folder[j],"/",folder[j],".clm2.h0.2013-10-24-00000.nc", sep = "")
  }else if (ntype[j]=="mo"){
        filename <- paste(rundir,folder[j],"/",folder[j],".clm2.h0.0", y[i], "-05.nc", sep = "")
  }else{
    print(paste("need to specify valid frequency of output for",folder[j]))
     break
    }

        in.file <- nc_open(filename)
        
#get the variables
if (ntype[j]=="dy") {
        for(k in 1:noutputs){
        in.soil[[k]][1:729] <- ncvar_get(in.file, out.string[k])
        }
}else{
        for(k in 1:noutputs){
        in.soil[[k]][(1+(i-1)*nskip[j]):(i*nskip[j])] <- ncvar_get(in.file, out.string[k])
        }
}  
        # remove the giant .nc file just so it's not taking up memory
        rm(in.file)
        
        print(paste("done with folder", folder[j], "done with year", y[i]))      
        index = index + 1
  }

deepmat[[j]] = in.soil
names(deepmat[[j]]) <- out.string
}
names(deepmat) <- folder
```

##Plot timeseries
```{r}
spinfolder <- folder[ntype=="yr"]
par(mfrow=c(2,2))
for(i in 1:length(out.string)){
  maxin <- NULL
  for(j in 1:length(spinfolder)){
  maxin[j] <- max(deepmat[[j]][[i]])
  }
  maxall <- max(maxin)

#The number of spinup dataset that will be plotted is hardcoded (2 in this example) - may need to modify
    plot(deepmat[[spinfolder[1]]][[i]], type="l",col="gray", xlab="Years", ylab=out.string[i], ylim=c(0,maxall))
    lines(deepmat[[spinfolder[2]]][[i]], type="l", col="black")
}

#GPP units: gC/m2/s
#From Falge et al. 2002 AgForMet
  #Blodgett Forest Seasonal Maximum GPP (umolCO2/m2/s) = 23.8 (DOY=159)
  #Blodgett Forest Seasonal Miniumum GPP (umolCO2/m2/s) = 7.6 (DOY=339)
  #Blodgett Forest Seasonal Maximum Re (umolCO2/m2/s) = 3.3 (DOY=343)
  #Blodgett Forest Seasonal Miniumum Re (umolCO2/m2/s) = 0.9 (DOY=257)
  #Blodgett Forest Annual GPP (gC/m2/yr) = 1386
s2y <- 60*60*24*365 #gC/m2/s to gC/m2/yr
mean(tail(deepmat[["NSC_ambient1"]]$GPP,100))*s2y
mean(tail(deepmat[["CEC"]]$GPP,100))*s2y
  #Blodgett Forest Annual NEP (gC/m2/yr) = 339
mean(tail(deepmat[["NSC_ambient1"]]$NPP,100))*s2y  #not quite NEP, but ok first pass in absence of disturbance
mean(tail(deepmat[["CEC"]]$NPP,100))*s2y

#check if total ecosystem C changes < 1% per year over a 30 year period
nyearbig <- nyear[nyear>31]
check <- rep(F,length(nyearbig))
for(i in 1:length(nyearbig)){
maxli <- length(deepmat[[i]]) #how many elements in list
maxit <- length(deepmat[[i]][[1]]) #how many elements in each list item
tot <- matrix(ncol=maxli,nrow=31)
for(j in 1:maxli){
tot[,j] <- deepmat[[i]][[j]][(maxit-30):maxit]
}
check[i] <- all(100*diff(tot[,i])/tot[1:30,i] < 1)
plot(100*diff(tot[,i])/tot[1:30,i], col=i, main=folder[i], type="o", xlab="Years", ylab="Delta SOC (%/yr)")
}
check
```

##Load seasonal monthly model output
```{r, eval=FALSE}
monfolder= folder[ntype=="mo"]
deepmat.1d=deepmat.2d.15=deepmat.2d.10=NULL
out.string.1d <- c("TOTSOMC","TOTSOMC_1m","TOTECOSYSC","TOTVEGC","LAISHA","LAISUN","GPP","HR","NPP","TSOI_10CM")
out.string.2d.15 <- c("SOILPSI", "HR_vr")
out.string.2d.10 <- c("CO2x_TRACER_CONC_BULK","POLYC_TRACER_CONC_BULK","MONOC_TRACER_CONC_BULK","MICC_TRACER_CONC_BULK","ENZC_TRACER_CONC_BULK","RESC_TRACER_CONC_BULK","LIT1C_TRACER_CONC_BULK","LIT2C_TRACER_CONC_BULK","LIT3C_TRACER_CONC_BULK")   
in.soil.1d=in.soil.2d.15=in.soil.2d.10=NULL

ytot <- 3 #total number of years run
yraw <- seq(1,ytot,by=1)
y <- str_pad(yraw, 4, pad = "0")
month.num <- c("01", "02", "03", "04", "05", "06", "07", "08", "09", "10", "11", "12")

for (j in 1:length(monfolder)) {
  for(i in 1:length(out.string.1d)){
  in.soil.1d[[i]] <- vector(length = ytot*12)
  }
  for(i in 1:length(out.string.2d.15)){
  in.soil.2d.15[[i]] <- matrix(nrow=ytot*12, ncol=15)
  }
  for(i in 1:length(out.string.2d.10)){
  in.soil.2d.10[[i]] <- matrix(nrow=ytot*12, ncol=10)
  }
  
  for (h in 1:length(y)) {

      for (m in 1:12) {
        filename <- paste(rundir,monfolder,"/",monfolder,".clm2.h0.", y[h], "-", month.num[m], ".nc", sep = "")
        in.file <- nc_open(filename)
        
        # get the variable
        for(k in 1:length(out.string.1d)){
        in.soil.1d[[k]][((1+(h-1)*m):(h*m))] <- ncvar_get(in.file, out.string.1d[k])
        }
        for(k in 1:length(out.string.2d.15)){
        in.soil.2d.15[[k]][((1+(h-1)*m):(h*m)),] <- ncvar_get(in.file, out.string.2d.15[k])
        }
        for(k in 1:length(out.string.2d.10)){
        in.soil.2d.10[[k]][((1+(h-1)*m):(h*m)),] <- ncvar_get(in.file, out.string.2d.10[k])
        }

        rm(in.file)
      }
  print(paste("done with year", y[h]))
  index = index+1
}
deepmat.1d[[j]] = in.soil.1d
deepmat.2d.15[[j]] = in.soil.2d.15
deepmat.2d.10[[j]] = in.soil.2d.10
names(deepmat.1d[[j]]) <- out.string.1d
names(deepmat.2d.15[[j]]) <- out.string.2d.15
names(deepmat.2d.10[[j]]) <- out.string.2d.10
}    

names(deepmat.1d) <- monfolder
names(deepmat.2d.15) <- monfolder
names(deepmat.2d.10) <- monfolder
```

##Load seasonal daily model output
```{r}
dayfolder= folder[ntype=="dy"]
deepmat.1d=deepmat.2d.15=deepmat.2d.10=NULL
out.string.1d <- c("TOTSOMC","TOTSOMC_1m","TOTECOSYSC","TOTVEGC","LAISHA","LAISUN","GPP","HR","NPP","CO2x_FLX_SURFEMI","TSOI_10CM")
out.string.2d.15 <- c("SOILPSI", "HR_vr")
out.string.2d.10 <- c("CO2x_TRACER_CONC_BULK","POLYC_TRACER_CONC_BULK","MONOC_TRACER_CONC_BULK","MICC_TRACER_CONC_BULK","ENZC_TRACER_CONC_BULK","RESC_TRACER_CONC_BULK","LIT1C_TRACER_CONC_BULK","LIT2C_TRACER_CONC_BULK","LIT3C_TRACER_CONC_BULK")   
in.soil.1d=in.soil.2d.15=in.soil.2d.10=NULL

#The output size for this experiment is hardcoded below (729 days) - may need to modify
for (j in 1:length(dayfolder)) {
  for(i in 1:length(out.string.1d)){
  in.soil.1d[[i]] <- vector(length = 729)
  }
  for(i in 1:length(out.string.2d.15)){
  in.soil.2d.15[[i]] <- matrix(nrow=729, ncol=15)
  }
  for(i in 1:length(out.string.2d.10)){
  in.soil.2d.10[[i]] <- matrix(nrow=729, ncol=10)
  }

        filename <- paste(rundir,dayfolder[j],"/",dayfolder[j],".clm2.h0.2013-10-24-00000.nc", sep = "")

        in.file <- nc_open(filename)
        
        for(k in 1:length(out.string.1d)){
        in.soil.1d[[k]] <- ncvar_get(in.file, out.string.1d[k])
        }
        for(k in 1:length(out.string.2d.15)){
        in.soil.2d.15[[k]] <- ncvar_get(in.file, out.string.2d.15[k])
        }
        for(k in 1:length(out.string.2d.10)){
        in.soil.2d.10[[k]] <- ncvar_get(in.file, out.string.2d.10[k])
        }

        rm(in.file)

deepmat.1d[[j]] = in.soil.1d
deepmat.2d.15[[j]] = in.soil.2d.15
deepmat.2d.10[[j]] = in.soil.2d.10
names(deepmat.1d[[j]]) <- out.string.1d
names(deepmat.2d.15[[j]]) <- out.string.2d.15
names(deepmat.2d.10[[j]]) <- out.string.2d.10
}
names(deepmat.1d) <- dayfolder
names(deepmat.2d.15) <- dayfolder
names(deepmat.2d.10) <- dayfolder
```
##Plot daily model output
```{r}
par(mfrow=c(2,2))
for(i in 1:length(out.string.1d)){
  minin <- NULL
  maxin <- NULL
  for(j in 1:length(dayfolder)){
  minin[j] <- min(deepmat.1d[[j]][[i]])
  maxin[j] <- max(deepmat.1d[[j]][[i]])
  }
  maxall <- max(maxin)
  minall <- min(minin)

#The number of datasets to be plotted here is hardcoded (ambient and warmed). Because these are diagnostic plots I did not include a legend. Gray is ambient and dark red is warmed +4C.
    plot(deepmat.1d[[dayfolder[1]]][[i]], type="l",col="gray", xlab="Days", ylab=out.string.1d[i], ylim=c(minall,maxall))
    lines(deepmat.1d[[dayfolder[2]]][[i]], type="l", col="dark red") 
}
```

#Model-data comparisons
##Initial profile comparisons with Blodgett data
```{r}
depth.m = c(0.00710, 0.0279, 0.0623, 0.119, 0.212, 0.366, 0.620, 1.038, 1.728, 2.865, 4.739, 7.830, 12.925, 21.326, 35.178) #modeled depth increments
depm = depth.m[1:10] #top 10 layers

summat = 12*(deepmat.2d.10[[dayfolder[1]]][["POLYC_TRACER_CONC_BULK"]] + deepmat.2d.10[[dayfolder[1]]][["MONOC_TRACER_CONC_BULK"]] + deepmat.2d.10[[dayfolder[1]]][["MICC_TRACER_CONC_BULK"]] + deepmat.2d.10[[dayfolder[1]]][["ENZC_TRACER_CONC_BULK"]] + deepmat.2d.10[[dayfolder[1]]][["RESC_TRACER_CONC_BULK"]])

micmat = 12*(deepmat.2d.10[[dayfolder[1]]][["MICC_TRACER_CONC_BULK"]] + deepmat.2d.10[[dayfolder[1]]][["RESC_TRACER_CONC_BULK"]])

#soil C profile
par(mfrow=c(1,1))
plot(df$g.C.m2/1000,df$Mid.Depth/100, col="gray", pch=16, ylab="Depth (m)", xlab=expression("Soil C to 1 m depth (kg C" ~m^-2~")"), ylim=c(1,0), xlim=c(0,10), main="Blodgett, CA")
legend("bottomright",c("Observed","Predicted"), col=c("gray",1), lty=1, pch=16, cex=0.8)
for(i in 1:729){
points(summat[,i]/1000,depm, type="p",col=1, pch=16)
}

#microbial biomass profile
df$MatchDepth <- df$Mid.Depth
meanm <- tapply(mbd$micgram, mbd$MidDepth, median, na.rm=T)
#micgram: mgC (g dry soil)-1 to gCm2
plot(mbd$micgram, mbd$MidDepth/100, pch=16, col="lightgray", ylab="Depth (m)", xlab=expression("Microbial C to 1 m depth (g C" ~m^-2~")"), ylim=c(1,0), xlim=c(0,800), main="Blodgett, CA")
points(meanm, as.numeric(as.character(names(meanm)))/100, pch=16, col="darkgray")
for(i in 1:729){
points(micmat[,i],depm, type="p",col=1, pch=16)
}

#CO2 gas concentration profile
meanf <- tapply(cf$CO2, cf$Depth, median, na.rm=T)
plot(cf$CO2,cf$Depth/100, col="lightgray", pch=16, ylab="Depth (m)", xlab=expression("[CO2] to 1 m depth (ppm)"), ylim=c(1,0), main="Blodgett, CA")
points(meanf,as.numeric(as.character(names(meanf)))/100, col="darkgray", pch=16)
for(i in 1:729){
points(deepmat.2d.10[[dayfolder[1]]][["CO2x_TRACER_CONC_BULK"]][,i]*44*1000*0.516,depm, type="p",col=1, pch=16) #conv mol/m3 to ppm
}
legend("topright",c("Observed","ReSOM"), col=c("gray",1), lty=1, pch=16, cex=0.8)
```

##Seasonal comparisons with Blodgett data
```{r}
summary(auto$lin_flux) #umol CO2/m2/s
u2m <- 12*1e-6*1000*60*60 #umol/m2/s to mgC/m2/hr
u2s <- 12*1e-6 #umol/m2/s to gC/m2/s
u2mol <- 1e-6*12/44 #umol CO2/m2/s to mol C/m2/s

#compare modeled and observed autochamber fluxes for ambient and heated
#the length of the experiment is hardcoded at 2 years
plot(control$time_series, control$lin_flux*u2mol, pch=16, cex=0.5, ylab="Autochamber Fluxes (molC/m2/s)")
points(heated$time_series, heated$lin_flux*u2mol, col=2, pch=16, cex=0.5)
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729), deepmat.1d[[dayfolder[1]]][["CO2x_FLX_SURFEMI"]], type="o",col="dark gray")
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729), deepmat.1d[[dayfolder[2]]][["CO2x_FLX_SURFEMI"]], type="o",col="dark red")

#compare modeled (10cm) and observed (5cm?) soil temperature
#output of TSOI_10CM is not different because I imposed a temperature change in resom only in order not to mess with the energy balance in the rest of the model
plot(control$time_series, control$soil_temp_C, xlab="Time", ylab="5-10cm Soil Temperature (C)")
points(heated$time_series, heated$soil_temp_C, col=2)
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729), deepmat.1d[[dayfolder[1]]][["TSOI_10CM"]]-273.15, type="o",col="dark gray")
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729), deepmat.1d[[dayfolder[2]]][["TSOI_10CM"]]-273.15+4, type="o",col="dark red")

#compared modeled soilpsi to observed vwc
par(mfrow=c(1,2))
plot(control$time_series, control$VWC, xlab="Time", ylab="VWC", ylim=c(-0.3,0.5),cex=0.3)
points(heated$time_series, heated$VWC, xlab="Time", ylab="VWC", col=2,cex=0.3)

plot(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729),deepmat.2d.15[[dayfolder[1]]][["SOILPSI"]][1,], type="o",col=rgb(0,0,0,1/10), xlab="Time", ylab="PSI",cex=0.5)
for(i in 1:10){
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729),deepmat.2d.15[[dayfolder[1]]][["SOILPSI"]][i,], type="o",col=rgb(0,0,0,i/10),cex=0.5)
points(x = seq(as.POSIXlt("2013-10-24 20:22:00 GMT"),as.POSIXlt("2015-12-24 20:22:00 GMT"),length=729),deepmat.2d.15[[dayfolder[2]]][["SOILPSI"]][i,], type="o",col=rgb(255/355,0,0,i/10),cex=0.5)
}
```

##Profile comparisons with Blodgett data
```{r}
#plot observed and modeled CO2 concentration for ambient and heated 
meanf <- tapply(cf$CO2, cf$Depth, median, na.rm=T)
meanh <- tapply(hf$CO2, hf$Depth, median, na.rm=T)
plot(cf$CO2,cf$Depth/100, col="lightgray", pch=16, ylab="Depth (m)", xlab=expression("[CO2] to 1 m depth (ppm)"), ylim=c(1,0), main="Blodgett, CA")
points(meanf,as.numeric(as.character(names(meanf)))/100, col="darkgray", pch=16, type="o")
points(hf$CO2,hf$Depth/100, col=2, pch=16)
points(meanh,as.numeric(as.character(names(meanh)))/100, col=2, pch=16, type="o")
points(deepmat.2d.10[[dayfolder[1]]][["CO2x_TRACER_CONC_BULK"]][,700]*44*1000*0.516,depm, type="o",col="dark gray", pch=16)
points(deepmat.2d.10[[dayfolder[2]]][["CO2x_TRACER_CONC_BULK"]][,700]*44*1000*0.516,depm, type="o",col="dark red", pch=16)
```

#Modeled Q10
```{r}
#plot modeled Q10 of heterotrophic respiration
q10mod = (deepmat.2d.15[[dayfolder[2]]][["HR_vr"]][,729]/deepmat.2d.15[[dayfolder[1]]][["HR_vr"]][,729])^(10/4)
plot(q10mod,depth.m, pch=16, type="p", col=1, ylab="Depth (m)", xlab=expression("Q10"), ylim=c(1,0), xlim=c(0,30), main="Blodgett, CA")
q10modinst <- matrix(nrow=729, ncol=15)
for(i in 1:729){
q10modinst[i,] = (deepmat.2d.15[[dayfolder[2]]][["HR_vr"]][,i]/deepmat.2d.15[[dayfolder[1]]][["HR_vr"]][,i])^(10/4)
points(q10modinst[i,],depth.m, col="darkgray", pch=16, type="p")
}
points(colSums(q10modinst)/729,depth.m, pch=16, type="o", col=1)
```

